\clearpage

% recipient data
\newcommand{\company}{Jacobs School of Music}
\newcommand{\positionName}{Software Engineer}
\recipient{\company}{Indiana University\\
107 S. Indiana Avenue\\
Bloomington, IN 47405}
\date{February 27, 2022}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}

\makelettertitle

I am writing to apply for the \positionName{} position with the Center for the History of Music Theory and Literature.
I have several years of experience writing software in C++ and Python and a strong desire to learn new skills,
and I feel that I would be a great fit for the position.

As my resum\'{e} shows, my degrees are in physics and mathematics. However, I
do have several years of experience as a software developer through my
involvement with several research teams, and through my personal projects. I
feel that this professional experience has given me strong software engineering
and related skills that make me a great fit for your open position. In
addition, my background in physics and math has given me excellent analytical
and problem solving skills. These skills are essential in the software
development field, and I believe that my background sets me apart as a unique
applicant.

I am most proficient and comfortable writing C++. Most of my professional
software development experience has involved writing C++, and I am familiar
with a variety of C++ programming styles, both old and new. I also have substantial experience with Python development and some experience with front and back end web development which I feel would be valuable in this role.

In addition to my software engineering experience, I have held other professional roles that make me particularly qualified for this position.
My work as a special collections processing assistant at Cornell University is highly relevant to this position, as my primary duties for that role were the digitization and cataloging of rare and manuscript items.
I also have a strong music background, as I was a professional musician for several years in middle school and high school.
I played hundreds of jobs over the summer in my family's band (which included my brother, a current Jacobs School of Music student).

I hope that you will consider me for your team, and I look forward to
hearing from you. Thank you for your time.

\makeletterclosing
